Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-05 manuscript/manuscript.Rmd
journal name

journal: "[journal]"
date: "`r Sys.Date()`"
bibliography: explain-pricing.bib
#linenumbers: true
numbersections: true
# csl: elsevier-harvard.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
layout: preprint, 3p, twocolumn, letterpaper, 10pt
---

@@

In our discussion, we adopt the organization of techniques and some notation
presented in @molnar2018interpretable and @biecekPMVEE, which are comprehensive
references on the most established ML interpretation techniques.

>>>>

journal: "Variance"
date: "`r Sys.Date()`"
bibliography: explain-pricing.bib
#linenumbers: true
numbersections: true
# csl: elsevier-harvard.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
layout: preprint, 3p, twocolumn, letterpaper, 10pt
---

@@

The techniques we utilize to answer these questions are permutation variable
importance, partial dependence plots, and additive variable attributions, 
respectively.
In our discussion, we adopt the organization of techniques and some notation
presented in @molnar2018interpretable and @biecekPMVEE, which are comprehensive
references on the most established ML interpretation techniques.
